---
layout: post
title: "Using Rmd files for Posts"
date:   2020-06-07
tags: [r, jekyll]
output:
  md_document:
    pandoc_args: ["--wrap=none"]
    variant: gfm
    preserve_yaml: TRUE
always_allow_html: true
editor_options:
  chunk_output_type: console
hidden: true
---

```{r setup, include=FALSE}
source(here::here("rmd_config.R"))
library(ggplot2)
# library(plotly)
library(dplyr)
library(tidyr)
library(kableExtra)
```

Some blog posts will require the use of data and data-driven graphics to convey information, so it would be helpful to incorporate R in creating blog posts while adhering to the style of the website, e.g., font style, background, etc. I experiment with `ggplot`, `kable`, and `kableExtra`.

I use [Jesse Cambon's blog post](https://jessecambon.github.io/2019/12/08/practical-tidy-evaluation.html) and the associated [Rmd file on GitHub](https://github.com/jessecambon/jessecambon.github.io/blob/master/_posts/2020-03-22-deploying-rmarkdown-online.Rmd) as a reference to incorporate Rmd files as blog posts.

## YAML header
```{r eval = F}
---
layout: post
title: "Using Rmd files for Posts"
date:   2020-06-07
tags: [r, jekyll]
output:
  md_document:
    pandoc_args: ["--wrap=none"]
    variant: gfm
    preserve_yaml: TRUE
editor_options:
  chunk_output_type: console
---
```


## Configuration File

In the root directory is a file called `rmd_config.R` which houses configuration settings for all Rmd files. These settings inform the default chunk options, as well as set the base directory in the root of the website. I can also include global functions and `ggplot2` settings. By including `source(here::here("rmd_config.R"))` in a setup chunk at the top of my Rmd files, I can access these settings.

## Formatting

Notice that the text and background color of the page is consistent with the website. However, ggplot and base R graphics are not by default. To solve this issue with ggplot, I create my own ggplot theme `theme_oakweb`.

Some lingering issues to fix or consider:

* learn about tooltips with `kableExtra`
* learn about interactive plots with `plotly` and `ggplotly()`
* change striped color of kableTable


## Including Plots

My ggplot theme `theme_oakweb` was created using [Joey Stanley's blog post](http://joeystanley.com/blog/custom-themes-in-ggplot2) so that the background and the text of the graphic would align with the website.

<!-- I also reference [Juuso Parkkinen's blog post](https://ouzor.github.io/blog/2014/11/21/interactive-visualizations.html) to try out `plotly::ggplotly()`.  -->

```{r sampleplot, echo=FALSE}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  ggtitle("Sample Plot") +
  xlab("Sepal Length") +
  ylab("Sepal Width")
# sampleplot
# ggplotly(sampleplot, session = "knitr")
```

## Including Tables

```{r echo = FALSE}
iris_table <- iris %>%
  group_by(Species) %>%
  summarize(mean_length = mean(Sepal.Length),
            mean_width = mean(Sepal.Width))

kable(iris_table,
      format = "html",
      col.names = c("Species", "Mean Length", "Mean Width"),
      linesep = "",
      align = c("l", "c", "c"),
      digits = 2) %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = FALSE,
                position = "float_right")
```

This table was created with `knitr::kable` and `kableExtra`. Unlike the html output, hovering over the table does not change the color of the rows, and since this is a static site, it might not be possible to include such options as "hover" and "responsive" in the bootstrap options of the kable table.
