---
layout: post
title: "Using Rmd files for Posts"
date:   2020-06-07
tags: [r, jekyll]
output: 
  md_document:
    pandoc_args: ["--wrap=none"]
    variant: gfm
    preserve_yaml: TRUE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# source(here::here("rmd_config.R"))
library(ggplot2)
library(dplyr)
library(tidyr)
library(kableExtra)
```

Some blog posts will require the use of data and data-driven graphics to convey information, so it would be helpful to incorporate R in creating blog posts while adhering to the style of the website, e.g., font style, background, etc. I use [Jesse Cambon's blog post](https://jessecambon.github.io/2019/12/08/practical-tidy-evaluation.html) and the associated [Rmd file on GitHub](https://github.com/jessecambon/jessecambon.github.io/blob/master/_posts/2020-03-22-deploying-rmarkdown-online.Rmd) as a reference to accomplish this.

## YAML header
```{r eval = F}
---
layout: post
title: "Using Rmd files for Posts"
date:   2020-06-07
tags: [r, jekyll]
output: 
  md_document:
    pandoc_args: ["--wrap=none"]
    variant: gfm
    preserve_yaml: TRUE
editor_options: 
  chunk_output_type: console
---
```


## Configuration File

In the root directory is a file called `rmd_config.R` which houses configuration settings for all Rmd files. These settings inform the default chunk options, as well as set the base directory in the root of the website. I can also include global functions and `ggplot2` settings. By including `source(here::here("rmd_config.R"))` in a setup chunk at the top of my Rmd files, I can access these settings.

## Formatting

Notice that the text and background color of the page is consistent with the website. However, ggplot and base R graphics are not by default. To solve this issue with ggplot, I create my own ggplot theme `r theme_oakweb`.

Some lingering issues to fix:

* create `theme_oakweb`
* check kable table
* posts by tag should not include Rmd file 
* include ggplot2 settings in `rmd_config.R`

<!-- try {% if post contains ".md" | if post contains ".Rmd" %} {% endif %} -->

## Including Plots

My ggplot theme `theme_oakweb` was created using [Joey Stanley's blog post](http://joeystanley.com/blog/custom-themes-in-ggplot2) so that the background and the text of the graphic would align with the website.

```{r pressure, echo=FALSE}
ggplot(pressure, aes(x = temperature, y = pressure)) +
  geom_point() +
  ggtitle("Sample Plot")
```

